---
title: "Portfolio, Churn & Customer Value"
author: "Hugo Cornet, Pierre-Emmanuel Diot, Guillaume Le Halper, Djawed Mancer"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography:
- biblio.bib
- packages.bib
biblio-style: apalike
link-citations: true
description: This research paper aims at modelling customer portfolio, churn and customer value.
---

```{r eval=FALSE, include=FALSE}
# setwd("C:/Users/pemma/Dropbox/M2 EE 2021 2022/COURS/3R/TEAM 2 AB PORTEFEUILLE/04 - RAPPORT/bookdown")
```


# Abstract{-#abstract}

This paper is being realized as part of our last year in master's degree in economics. It aims at studying the firm's most valuable asset: its customers. To that end, we adopt a quantitative approach based on a mix of Econometrics and Data Science techniques with a threefold purpose:

- Model customer *portfolio* as a set of customer segments; 
- Predict and analyze customer *attrition*; 
- Estimate customer portfolio's overall *value*.

After having defined the subject's key concepts, we apply duration models and machine learning algorithms to a [kaggle](https://www.kaggle.com/yeanzc/telco-customer-churn-ibm-dataset) dataset related to customers of a fictional telecommunications service provider (TSP).

***Keywords***: *customer portfolio management (CPM), churn, customer value, duration models, machine learning, telecom.* 

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```



<!--chapter:end:index.Rmd-->


# Introduction {#intro}

Placeholder


## How to define a customer portfolio? {#portfoliodef}
## What is attrition? {#attritiondef}
## What does customer "value" mean? {#valuedef}

<!--chapter:end:01-intro.Rmd-->


# Literature Review {#literature}

Placeholder


## On customer portfolio {#portfolio}
## On attrition {#attrition}
## On customer value {#value}

<!--chapter:end:02-literature.Rmd-->


# Duration models {#duration}

Placeholder


## Definition
## Censoring and Truncation
### Censoring mechanisms
### Selection bias
## Probabilistic concepts 
### Survival function
### Hazard and Cumulative Hazard functions 
## Nonparametric models {#nonparam}
### Notations
### Hazard function estimator
### Kaplan-Meier estimator
### Nelson-Aalen estimator
## Parametric models
### Constant hazard (exponential model)
### Monotone hazard
#### Weibull model {-}
#### Other models {-}
### Concave and convex hazard
## Semi-parametric estimation 
### *Proportional Hazards* models
#### What does *proportional hazards* mean? {-}
#### Marginal effects {-}
#### Partial likelihood estimation {-}
### Cox PH model
## Performance metrics
### Concordance index (C-index)
### Brier score

<!--chapter:end:03-duration.Rmd-->


# Machine Learning {#ml}

Placeholder


## Machine Learning for Survival Data
### Survival Trees
### Random Survival Forests (RSF)
### Cox Boosting
## Regression methods
### Linear models
#### Model formulation {-}
#### Ordinary Least Squares {-}
#### Regularization {-}
#### Gradient Descent {-}
### More advanced regression models 
#### Generalized Additive Model (GAM) {-}
#### Other models {-}
## Performance Metrics
### Metrics for Regression models
#### Notations {-}
#### Coefficient of determination {-}
#### Mean Squared Error (MSE) {-}
### Metrics for Survival models
#### Concordance index (C-index) {-}
#### Brier score {-}

<!--chapter:end:04-ml.Rmd-->


# Data {#data}

Placeholder


## General Overview
## `Churn_Value` and `Tenure_Months` 
### Demographic data {-}
### Data on services subscribed {-}
### Customer account data {-}
## `CLTV`: Customer Lifetime Value
### Demographic data {-}
### Data on services subscribed {-}
### Customer account data {-}
### Correlation between `CLTV` and explanatory quantitative variables {-}
## Churn, duration and customer *value* 

<!--chapter:end:05-data.Rmd-->


# Estimation techniques 

Placeholder


## Portfolio segmentation 
## Churn prediction 
## Estimation of portfolio value 

<!--chapter:end:06-estimationtechniques.Rmd-->


# Appendix {-#appendix}

Placeholder


## Hazard function {-}
## Link between cumulative hazard and survivor functions {-}
## Contribution to the partial likelihood function in PH models {-}
## Partial likelihood function in PH models {-}

<!--chapter:end:07-appendix.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:08-references.Rmd-->

