---
title: "Portfolio, Churn & Customer Value"
author: "Hugo Cornet, Pierre-Emmanuel Diot, Guillaume Le Halper, Djawed Mancer"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography:
- biblio.bib
- packages.bib
biblio-style: apalike
link-citations: true
description: This research paper aims at modelling customer portfolio, churn and customer value.
---

```{r eval=FALSE, include=FALSE}
# setwd("C:/Users/pemma/Dropbox/M2 EE 2021 2022/COURS/3R/TEAM 2 AB PORTEFEUILLE/04 - RAPPORT/bookdown")
```


# Abstract{-#abstract}

This paper is being realized as part of our last year in master's degree in economics. It aims at studying the firm's most valuable asset namely its customers. To that end, we adopt a quantitative approach based on econometrics and data analysis with a threefold purpose to: 

- model *customer portfolio* as a set of customer segments; 
- predict and analyse customer *churn*; 
- estimate customer portfolio's overall *value*.

After having defined the subject's key concepts, we apply duration models and machine learning techniques to a [kaggle](https://www.kaggle.com/yeanzc/telco-customer-churn-ibm-dataset) dataset related to customers of a fictional telecommunications service provider (TSP).

***Keywords***: *customer portfolio management (CPM), churn, customer value, duration models, machine learning, telecom.* 

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


